---
title: "Recognition of the NMIST handwritten digit dataset using convolutional neural networks"
output: html_notebook
---

The original data can be downloaded from [NMIST](http://yann.lecun.com/exdb/mnist/).
The current notebook uses the data set from the package *Keras*.


<!-- Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*.  -->

<!-- Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*. -->

<!-- When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file). -->

<!-- The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed. -->


Let's follow the example on Chapter 2 of Deep Learning with R, 2018, by Francois Collete and J.J. Altaire.


```{r}
library(keras)
mnist <- dataset_mnist()
train_images <- mnist$train$x
train_labels <- mnist$train$y
test_images <- mnist$test$x
test_labels <- mnist$test$y
```

## Data exploration

Let's look at the tensors in the data set. First the training data:

```{r}
str(train_images)
str(train_labels)
```

The images are stored in a 3d tensor of integers of dimensions 60000 x 28 x 28.
The labels in a 1d tensor of intengers of dimensions 60000 x 1 containing the digits the respective image represents.

And then the test data:

```{r}
str(test_images)
str(test_labels)
```

The test images are stored in a 3d tensor of integers of dimensions 10000 x 28 x 28.
The tes labels in a 1d tensor of intengers of dimensions 10000 x 1.


## Workflow

First the training data will be fed to the neural network. Then it will learn to associate an image with a label. Finally thye neural network will be asked to predict the labels for the test images, and a verification of how well the prediction is will be made.




